\section{Beez}\label{sec:donovanDrappus}
\race{Half-orc} \class{Cleric} \player{Al} \medskip
\headeritem{Given name}{Brukzhul}
\headeritem{Known alias}{John Smith}

16
10
16
9
15
8

AC 13
HP 11

\hrulefill
Player-written background:

On your way through town, you stopped at the bar your friend recommended -- out of the way, known to the locals, only good brews for serious drinkers. Coming through the door, you see the obviously competent bartenders quietly keeping the place running. You hear the bard from the corner of the room playing for those who want to listen and providing the perfect amount of ambient noise to keep intimate conversation private. The place is warm and welcoming, and you are glad you stopped by.

But you are stopped short when you see the halfbreed at the end of the bar, and are immediately disgusted with your initial reaction to tha--him. You didn't grow up around any of their kind, and in spite of your liberal leanings you feel your heart-race increase and your palms start to sweat. You always assumed yourself to be above this sort of snap-judgment and took that assumption as enough.

Then you start to panic, and like a race-wagon that starts to spin your instinct is to overcorrect. You paint on an obviously forced smile, walk over to his side of the bar, pull up a stool and attempt casual conversation.

Stop.
---
I saw you as you walked in, took stock and adjusted my night’s plans accordingly. I watched the revulsion wash over you as you noticed me, and while I appreciate your ultimate realization that good thoughts can’t fix a lifetime of immersion in prejudice, fix that shit on your time. I’ve done my best to be inconspicuous, but I need to be on hand as a deterrent to the less civilized folks that occasionally wander in. It doesn’t happen often, so my plan for the night is to sit and drink. Stay wary enough to do my job, exchange a few professional courtesies with the regulars and drink. I’m not your therapist, I’m not your echo chamber and I’m not your friend. Feel free to enjoy the bar, but kindly fuck off and do it elsewhere.
------------------------
Quick life story. Raised in a poor part of town to an Orc mother and unknown human father. Birth name Brukzhul after an important figure in mom’s life. Dad brought them to the city, then quietly disappeared from their lives. BZ was always an outsider, and while he found a few friends here and there he constantly faced prejudice, both overt and subtle.

In an effort to find some sense of belonging BZ took the king’s coin as a young man, enlisting as John Smith. He worked tirelessly to prove himself worthy. After a few commanding officers noticed his medical/healing abilities and his dedication to his fellow soldiers, John Smith was given command of a small crew. In these fighters he inspired fierce loyalty. They knew he would always be right there with them in the melee, and he would never order them to do something he didn’t firmly believe in. This is the closest thing to a family John found.

But the prejudice and racism hounded him. Other squads were more than happy to fight alongside John and his crew, known throughout the army as The Landslide. They swept through the fight to where they were needed and built a wall of will to protect. When the fighting was done they were at best ignored and occasionally outright insulted. John never let an insult pass unanswered, and occasionally skirted the military code of conduct in an attempt to correct his more outspoken offenders. It never stopped.

The stings all add up. It wasn’t a single devastating event, but a lifetime of needle pricks and occasional dagger wounds. As he saw it, there were two ways to handle this. He could either fold and let them win or harden up and rise above. He opted for the latter path and tried to callous himself against the insults -- to prove he was worthy of better treatment. As he steeled himself against offense, both intentional and unintentional, he also distanced himself from his crew. He spent more and more offtime on his own, hoping to save them from being too closely associated with him, until he found himself once again on the outside. He still fiercely protected his crew in battle and took pride in his leadership abilities, but his isolation was nearly complete by the end of his career.

He always blamed himself for not being promoted above commanding the single crew. A higher rank would have offered John a sizable retirement situation and greater respect. But his immediate superior, who spent his time fighting for John in ways John would never realize, knew the truth. When it came time to discharge John, Superior made sure he had a decent retirement package to take with him.

John went back to the city he grew up in. He wasn’t really close with his mother, but not being there when she passed never sat right with him. He took a few of his military issued items when he left, but on the trip he scratched his crew’s insignia from the shield and shed his name. His orc name never felt right, and John Smith was too heavy to keep carrying around. He started introducing himself as Beez.

Once he was back in the city, he found the bar he intended to spend the last leg of his life in. He built a relationship with the owners. Let let him buyout the small apartment over the bar and work as a bouncer in trade for food and drink. His presence was intimidating enough to keep most folks in line, and those few who stepped out were dealt with handily.

His relationships were functional. He cared greatly for the bar’s staff and the few regulars who meshed with him, and Beez was always there for them. But he never allowed himself to ask for reciprocation, never opened up, barely told his story. Most everyone knew he was a soldier, and a few knew he grew up around the city.

This is where we find him.


