\section{The Empire}
\headeritem{Structure}{Feudal Monarchy}

The yuan-ti established an empire but were driven out, slaughtered wholesale.
Some few escaped east, into the Tribal Wastes.

\subsection{Culture}
\subsubsection{Race Relations}
The Empire was founded in driving out the violent beast races.
While non- and half-humans are recognized all the rights of citizens, an attitude of human
 superiority pervades.

Elves are viewed as exotic novelties, despite many having been born and raised within Empire cities.
Half-orcs struggle to find work beyond menial labor.
Dragonborn, Aasimar and Tiefling tend to wear robes to keep their face and features hidden.

In cities, non-humans will have their own neighborhoods.
These aren't the slums common to third-class citizens, but intermixing is rare.

\subsection{Military}
Each baron must raise and maintain their own armed forces.
Each baron's force is divided into divisions.
A number of divisions are given to an impartial command, answerable only to the high Lord Admiral
 of The Empire and his Lord Marshals, in proportion to the size and population of the barony.
However, to discourage predictably disingenuous behavior in the peerage, the choice of which
 divisions serve The Empire and which are kept under the direction of the baron is made
 annually by the Lord Marshals.

\subsubsection{Armed Ranks}
Footman \textrightarrow
Knight \textrightarrow
Sergent \textrightarrow \ldots

\ldots \textrightarrow
In semi-limbo and generally self-supervised:
Warrant Officer, a title by a magistrate, decree, or other (generally political)
  appointment rather than rising through the ranks.
Typically has strings attached.

\ldots \textrightarrow
Lieutenant \textrightarrow
Captain

\ldots \textrightarrow These titles usually come with land, rights to council, etc:
Baron \textrightarrow
Lord Marshal \textrightarrow
High Lord Admiral

\subsection{Auxiliary Ranks}
Ensign \textrightarrow
Corporal \textrightarrow
Sub-captain

The sub-captain answers to a military captain but otherwise generally has free reign of operation.

\subsection{Arcane Ranks}
Apprentice \textrightarrow
Adept \textrightarrow
Erudite \textrightarrow
Master \textrightarrow
Grand Master

The Arcanum is never explicitly granted lands nor political council and is intended to be a
  neutral party.
There is a balancing act surrounding a Arcanum's obligation to military service with its holdings
  which are technically rented at the pleasure of the Emperess.
