\section{Preface: Jo'am meets a stranger}\label{sec:joamMeetsAStranger}

\begin{multicols}{2}
  \subsection{A visit to Gran's}
  \begin{aloud}
  It's late morning on a pleasant mid-spring day.
  It rained last night, so you think today might be a good day for foraging.
  At some point, you wander towards Gran's.

  As you walk down her road, you pass a merchant in a cart coming from her house.
  It's strange, because hardly anyone is willing to come past the edge, this close to the rag line.
  A young human male is driving the cart.
  He's wearing a bright blue askot, a wide floppy hat, and otherwise simple travel fare.

  What happened: Jo'am pet the horse for a while, said ``Hello BlueMan.''
  Eventually got nudged out of the way.
  \end{aloud}

If Jo'am stops him, the merchant-boy Jerome will chat.
He crossed the rag line last night fleeing cultists.
The askot is gran's threat against him if he violates his $geas$.
If commented upon, he's lie, probably poorly, but not discussing it is part of the $geas$.
He is more than happy to sell Jo'am any simple fare he might ask for.


Continuing to Gran's:

  \begin{aloud}
  As you approach Gran's cottage, everything feels right.
  The bees are buzzing around their boxes, the goat is in his pen, goating.
  As you approach, you notice the front door is slightly ajar.

  What happened: Jo' let himself in, hollered a hello, but otherwise sat down to watch gran's game.
  \end{aloud}

Calling out gets no response.
Depending on Jo'am's reaction, he might interrupt the next bit.

  \begin{aloud}
  Gran is at her table in the middle of the room, muttering to herself and playing her
    funny card game.
  She looks up as you enter, nods at you and offers a flickering smile, but doesn't interrupt
    her game.
  This isn't the first time you've walked in while she's busy like this, and you know it won't
    take long for her to finish.

  What happened: Succeeded on most of the first spread, some of the second,
    just dungeon and demon of the third.  Maybe also Yuan'ti dreadlord.
  \end{aloud}

If he stays to watch, show him the cards.
Each stack should have a DC 12, +1 per card, for him to see a flicker of the future.

Afterwards, Gran chews her lip a bit.
Seeming distracted, she still greets Jo'am  properly, offers him what's left of breakfast or tea.
If asked about Jerome, she'll say he was just a passing merchant.
If pressed, she'll joke about how he must've sensed her charm even from the main road.

After a moment, she'll look over at her windowsill tangle and frown.
One of the threads has come loose and is flapping in the wind.
DC 12 WIS + INT to realize that there isn't any wind, which Jo'am has ``always thought funny''
that the tangle would do that.

Seconds later, another strand comes loose.
Gran curses.
The cards have been left out.
She glances between them, the tangle, and Jo'am.

``Could you do your gran a favor?
While you're out today, go check on your friend Smit.
If he's got any venison cured, I'd take as much as he's willing to sell.
Tell him it's my money so he doesn't cheat himself thinking he's doing you a favor.''

  \begin{aloud}
What happened: Joam cleans up after himself, gathers his things carefully, takes the tangle
  because he's going to fix it.
\end{aloud}

\subsection{Wandering the Woods}

Try to gauge how distracted and noisy Jo'am is.
Perception to determine how far away his token is.
Ask if he's traveling along, in, or just kind of close to the stream.

Some distance away, he hears the sounds of struggle.
One man is standing in the stream, shouting at the other man.
``You agreed though, we both did.
  Are you a liar?
  We just have to do what it says.
  We have to.''
The other man is holding someone's head in the stream.
He is shounting, too.
``You have to take it, you have to, you have to, I want it out, he says he'll leave.
I changed my mind, I don't want it, get it out get-it-out getitout gititoutgititoutgititout!''

When they notice Jo'am, they are distracted and the man being held under surges free.
It is bound at the wrists.
It is Smit.

What do you do?

\begin{aloud}
  What happened: The drugs are starting to hit.
  Dig into a big rock, find some yummy moss.
  Hear splashing and shouting down the way.

  Smit and Crazy Man A tussle on the ground a bit.
  A swings and misses, driving his knife into the soft ground.

  Jo and Crazy Man B swing it out.
  Jo shouts about helping get rid of the bad spirits.
  B thinks he's going to help until a heavy, two-handed swing almost bowl him down.
  Alarmed, he stabs at Jo, glancing a blow off his walking staff but failing to bite into the meat of him.
  Jo responds more carefully this time, with a full-forced blow sideways across B's jaw.
  B holds his bleeding face, Jo kicks him into the stream.

  Meanwhile, Smit headbuts A's nose, spraying blood but otherwise not disabling A.
  Jo runs across to help.
  A, seeing this and his pummeled ally, scambles to his feet and starts to flee.
  Jo swings his staff and sends A stumbling to the ground.

  B has gotten to his feet.
  Jo asks ``Bad spirits gone?''
  B replies ``No, we agreed, he'll never leave, that's what we promised, we're not liars.''
  Jo goes to get rid of the bad spirits.

  Smit, seeing the man who held him in the stream mewling on the ground, delivers several kicks
    to A's head.
  Jo brings his staff down once more.
  With a sickening crack, B's face caves inward.
  Blood splatters.

  The drugs hit.
  Jo can feel every drop of blood spray across his face.
  Drop.  drop.  drop.
  One droplet lands in his eye, and the world turns red...
\end{aloud}

  \subsection{A guest}
As the last cultist dies, blood spatters into your face and mouth.
Time dilates.
Something is speaking to you inside your head.
It's different from how the spirits usually talk to you.
They usually use your own voice and words.
This one uses ideas to speak, but it's stumbling and jumbled.
With each phrase, you imagine something like the mess the bottom of a tankard leaves --
  a splattered circle -- and you know somehow that the different splatters are the phrases, too.


\begin{verbatim}
Self :: Joy ; Greeting > Start + Host
Self :: Optimism ~ Friendship < Host
Confidence . Secret && Incumbent + Host
< Dissatisfaction + Disappointment ~ Fragility
Observation && Host :: Fortitude < Compliment
Question && Host :: Willingness ~ Tenancy < Self
\end{verbatim}

After you accept, time seems to lurch back into place.
Smit is sitting, heaving breaths.

  \begin{aloud}
  What happened:  Pretty readily accepted the ``Blood Spirit'' into the back of his head.
  \end{aloud}

  \subsection{Aftermath}
Smit is shaken.
``They were going to kill me.''
Hopefully, Jo'am will help get him steady.

``See me home, would you?''
Recover a deer that Smit had shot.
He holds his knife and looks at the deer, unsteady.
``I don't suppose you can dress a deer?''
Maybe throw up in the stream.

Carry it the rest of the way down the stream to Smit's hut.
Or maybe they abandoned it.
Smit changes clothes.
Maybe they bum around a bit.
Smit goes stir crazy.
``Stomah's fucking fury, man.
  I'm going to the bar.
  You in?''

Play that scene by ear.

At some point, you go home.
Or not.
Maybe you're just wandering the woods now.
Let's find out.
But you cross the rag line, maybe on the shortcut you always take home, maybe on accident.

  \begin{aloud}
    What happened:
    Wander to smits shacks and cabin.
    Big man Jo has man-handled a deer carcass back to the shacks, where Smit hastily dressed it.

    They look the mess.
    gotta go to the bar.
    Jo puts on some of Smit's several-sizes-small clothes.

    On the way to town, Jo remembers to ask for cured venison.

    They get drunk.
    ``I met a blue man!''

    Stumble back to the cabin.
    Forget about the venison.

    Wander back half an hour later.
    Wake the loudly snoring Smit.
    Get some venison.
    Return to Gran's, after a full day.
  \end{aloud}

  \subsection{A Ragged Witch Appears}\label{subsec:scene:ARaggedWitchAppears}

  \begin{aloud}
  You look at the red ribbons hanging from the trees that mark the rag line.
  As you cross, they crack like they're in a gale wind.

  Her gravely voice seems to come from everywhere at once.
  ``You must know that to trespass means death.''
  You see her, the Ragged Witch, not far from you.
  Her tattered robes whip around her.
  ``My laws are absolute.''
  She lifts a hand at you, approaching closer.
  ``You have brought this on your own --
    Jo'am?!''

  Instantly, the winds die down.
  The tattered robe melts into gran's cloak.
  She runs up to you but stops short.
  ``Jo'am?''
  She looks you in the eye.
  ``What have you done to my Jo'am?''
  \end{aloud}

  \begin{aloud}
    What happened:
    ``Bad spirits out tonight gran.''
    Remembers to give venison and the ``fixed'' tangle.
  \end{aloud}


  Converse.

Gran is sad, but Jo'am has to leave.

``Will you come with me?''

Teleport.
You're on a road somewhere.
A cart is trundling down the path.
Gran gives Jo'am a bright red strip of cloth,
``As long as you keep this, I'll be watching over you.''

\subsection{On the road}\label{subsec:scene:OnTheRoad}
  Your driver has a lightning blue askot and a floppy hat.
  You head east.
\end{multicols}
