\section{Preface: Donovan is given a choice}\label{sec:prefaceC:DonovanIsGivenAChoice}
\begin{multicols}{2}
\subsection{Traveling to the Western Front}
  \begin{aloud}
  To the west lies the Legion of Ayanum, but everyone calls it the Horde.
  From the rumor mill, you've heard that they're generally xenophobes and have a very magic-focused
    culture and political system.
  You've heard that the country is ruled by a lich, you've heard that it's ruled by a dragon,
  you've heard that it's ruled by a parliament, you've heard that it's ruled by whatever
    wizard killed the last guy in power.
  You know, the rumor mill.

  About a year ago, they sent an emissary to the capital.
  They met with the Emperess and her council.
  Word never got out what they talked about, but they left unhappy.
  Ever since then the military has been shoring up it's western front.
  You've heard that political channels are still open, but it's clear that things in the west are
    headed south, as it were.

  You are driving one of many supply wagons in a long train on the way to the western front.
  It's the early days of summer, and it's been blessedly dry.
  As good of weather as you could hope for, when you have to sit behind a team of horses,
    trundling along slower than you would walk.
  \end{aloud}

DC 20 Vehicle (Land, Wisdom) check.  Wobble.

  \begin{aloud}
  Up ahead, you see a Tiefling off to the side of the road,
    walking so leisurely that your wagon is actually catchup up on them.
  They have their thumb out in the inter-universal symbol of the hitchhiker.
  Most humans are jumpy around teiflings, and as a result most tieflings tend to wear nondescript,
    baggy robes and hooded cloaks to hide their infernal features.
  But this one is just hanging out, skin the color of actual copper, horned head held high,
    hair the blue of veins hanging down, tail swishing as they walk.

  A few wagons ahead, someone upturns a pitcher of something at them.
  They dodge back in time, and while you can't hear the words that are exchanged, it's pretty clear
    the meaning.
  The tiefling tosses their pack onto the ground, taps their chest and holds their arms out in
    an invitation to fight.
  The other wagon keeps moving.

  After the wagon's moved on, the tiefling picks up their pack and, noticing the muck, deflates
    a bit.
  She turns around, and you're close enough now that she catches your eye, looking at you with
    those solid-color tiefling eyes, hers silver.
  She smiles hopelessly, raises her eyebrows, and sticks out her thumb.
  \end{aloud}

DC 20 Vehicle (Land, Wisdom) check.  Something feels off.

Shoot the shit for a while.

Goldie (get it?).
Raven necklace.
Arcanist.

DC 15 Vehicle (Land, Wisdom) check.  Advantage if passed either the previous two.

Throw a wheel.

DC 25 to be fine.

On fail, DC 20 to break down in the trail.

On fail, DC 15 to avoid capsizing.

On fail, DC 10 to avoid crippling one of the horses.

On anything other than a 25 success, Goldie takes off.
``No offense, but neither of us needs me here when your officer gets here.
See you around, big guy.''

If he brings it up, she'll magic it fixed quickly on a DC 20-success.

\subsection{A deserter needs aid}
Perception 18 to not be surprised while taking a shit.

An westerner is staring at you, wounded and dehydrated.

\subsection{A breathy visitor}
Goldie shows (back) up.

Chat, get an Message, ``grab your bag, we've gotta move.''

The Breath is not an emmasary of war, he's a messanger.

  \begin{aloud}
  ``You misunderstand.
    We do not wish for there to be conflict between us.
    We do not wish for there to be \emph{contact} between us.
    This country and its people are of a disease,
      and if it cannot be cut out, we must not allow it to spread.''
    The humans scowl, while the dragonborn's aide whispers something to him.
  ``I apologize.
    It appears I neglect some of your language's nuance.
    I speak neither metaphor nor insult.
    Our augers have forseen a plague borne from your empire, a disease of blood and of mind.
    We will not allow the pathogen within our borders.
    Your leaders refused our aid in rooting it out, and in respecting your nation's sovereignty,
      we are left at an impasse.''

  ``So what does all of this have to do with you massing your army at the border?''
     asks the Captain.
  ``As I said, you misunderstand.
    You see not an force of invasion, but one of defense.
    Any living thing that approaches the Dragonlands will be swiftly summarily executed.
    Our sorcerers will scorch their bodies and the earth beneath them.
    Our archers will kill every buzzard that would eat their flesh.
    Beginning now, \emph{nothing} [beat] enters the Dragonlands.''

    He speaks the next words quickly and reverently, as if reciting a prayer.
  ``My words are carried on the breath of the Gold Dragon,
      whose wisdom is boundless, whose word is law, and whose will is absolute.''
  \end{aloud}

  He's not going back.
  ``If my lord requires my life, I give it gladly.''



\subsection{Scene: A dream}

A woman, a cloak, a raven.

It cocks its head at you, questioning, considering, offering.

\subsection{You awake.}

Carnage everywhere.
You are the only survivor.

If you saved a life, you see their corpse.

If you saved an easterner, you see their corpse.

You wander back to camp

\subsection{Scene: A healer is given a choice}

Promotion to Warrant Sergent, conditional on reporting to Celadir's Bastion.

\end{multicols}
