\section{The Four Defenders -- The Origin of the Empire}

\textit{This is a story told throughout The Empire, by bards in barrooms, by youths around
  campfires, and by parents to their children.
The Four Defenders are revered almost as gods for their foundational importance.}

In the days before the Empire, we warred with the beastman constantly.
Herders worried less about wolves taking sheep than they did about gnolls taking their lives.
These dark, harsh times made dark, harsh people.
People like Stomah.

Stomah rose from the glowing embers of her ruined village with nothing but a sword and a promise:
  the beastmen would pay.
She traveled from town to town, taking the long and dangerous paths.
In her wake, the beast-tribes burned.
Gnolls lay be the roadside, gnarled and twisted.
Kobold caves filled with fallen, each one cracked and broken.
Lizardmen lay lascerated, bullywug bodies bloated.

In every city Stomah visited, every town, every village, every hamlet,
  men and women would join her.
Men and women made their own promises and took up their own swords.
She lead them onward, always along the long and dangerous paths.

Stomah and her warriors pressed onward.
Before their blades, the beastmen fell.
Before their wrath, the beastmen fled.

###
Stomah came to rely on several in her ever-growing host of followers.

The Raven, an elf with skin of charcoal and ash.
Tattered robes covered tattooed whorls, whirled and roiled when she cast her spells.

Celadir, a confidant and advisor to Stomah.
The half-Elf would later be named The Regent, though he wouldn't know it at the time
  and refused acknowledge it later.

The Wrecker, a half-Orc tinkerer,

A Wrath, a man whose fury and skill with a blade was second only to Stomah herself.


####
The host driven east.
Stomah pursued.
Celdadir voiced concern about exposing themselves.
Stomah orders her four most trusted warriors, advisors, friends to stay.
The rest of the host pushes north.

The Yuan-ti, the serpent-men, are as devious as they are vile.
Stomah is assassinated.
The Yuan-ti descend upon the western banks of the river.
They are not prepared.

The Raven, The Wrecker, The Regent, The Wrath, score a line in the earth.
Those abominations that dared to cross it were mete a brutal reward.

The Yuan-ti horde flowed for ages, but the fervent fury of the four was unending.
