\section{Ogden and Goldie}\label{sec:ogdenAndGoldie}
\headeritem{Also known as}{The Warrior and the Waif}

Ogden and Goldie are an adventuring duo, non-romantic couple that frequently crosses paths with
The Group.
Their path often intersects with The Group's between adventures, as they have gone on their own
adventures in the meantime.
Ogden and Goldie will perhaps pick up the adventures that The Group turns down, progressing
critical plot points in tandem.

They are almost comical in their night-and-day contrast to each other, sharing only that they are
both absurdly gorgeous, both favor studded leather armor in combat and loose clothing in social
situations, and both wear pendants of the Raven Queen.

\subsection{Ogden}\label{subsec:ogden}
\headeritem{Race}{Aasimar}
\headeritem{Voice}{Gaston}

  \begin{aloud}
  \label{description:ogden}
  Ogden looks like a fairytale prince had a bad run through the gladiator pit.
  His tan skin is practicably radiant, but covered with a patchwork of scars.
  He strong shoulders and broad frame collapse inward as he hunches.
  His lustrous blonde hair keeps a bounce even during combat, but is shaved down to stubble on
    the right with a jagged rune etched in.
  His eyes are as blue as the sky, but constantly twitch over the terrain, watching for, or perhaps
    searching for, a threat.

  Three parallel scars, an apparent claw mark, run down his neck and collarbone over over his heart.
  A tattoo of gills covers, or maybe accents, the scars.
  His brash attitude and tattoo combined to give him and, by relation,
    the adventurer band he fronts the nickname ``The Crazy Kuo-toa.''

  Ogden carries on his person enough steel to arm the entire band,
    and he carries very little beside.
  His glaive rarely leaves his hand.
  Two longswords cross on his back.
  A trio of sheathed daggers are strapped to either thigh.
  \end{aloud}

Wields a glaive and carries two longswords "just in case."
\dmonly{Pack of the Blade: the glaive.
Use Gladiator stat block plus minor spellcasting, set CHA to 18, CR 5+}

\subsection{Goldie}\label{subsec:goldie}
%% Wildly out of date.
Small, thing, quiet, and platinum blonde.
Sorceress, wields a quarterstaff as necessary.
\dmonly{Pack of the Tome: grants Fire Bolt, Dancing Lights, Ray of Frost}
\dmonly{Use Mage stat block, swap in some Warlock spells,
consider Studded Leather Armor, set Cha 18, CR 6+}
\subsection{Plot points}\label{subsec:plotPoints}
\dmonly{
Ogden and Goldie are both in truth warlocks of the Hexblade.
After the Act I arc, The Group will be invited to a high society gala to celebrate
their successes.
Goldie will distract the court magus with conversation and a low-cut dress.
Ogden will speak with one or more members of The Group.
After a lull, Ogden will sigh and excuse himself with the following.

``[sigh] Well, I should probably get to it then.
I've enjoyed our conversations over the past weeks.
No, I mean it.
I'll remember you fondly, no matter what.
[pause]
I hope you do the same.''

He walks towards Goldie, who looks up.
He nods at her.
Simultaneously, she summons her warpick and he his glaive.
She caves in the skull of the magus while Ogden sheers the head off of Plot Target.
Both flee immediately, mist
}

