\section{The Hellfish}
\headeritem{Also known as}{The Crazy Kuo-toa}

The Crazy Kuo-toa is an adventuring band that patrols the Eastern Wastes near the Bastion.
They track movement of the beast tribes, provide warning if it looks like they'll attack, and will
  help clear the area of more pressing threats, often with reinforcements from the Bastion.
Their frontman, the Aasimar Ogden, and the ranger Gluri
\subsection{Members}

Frontman:
\hyperref[subsec:ogden]{Ogden}.

Leader and general plus-one to whatever needs doing: Gluri Frosthand.

Relatively new scout:
\hyperref[subsec:buddyhawks]{Spacky ``Buddyhawk'' Dunderklump}.

Muscle:
Alotel Lithtaur

Runner, Messanger, and half-assed minstrel:
Garr Bolbec

\subsection{Gluri Frosthand}
\headeritem{Voice}{Gruff, curt, curses like a sailor.}
\headeritem{Statblock}{Duergar, minus sensitivity and innate magic}
% http://npcgenerator.azurewebsites.net/

Gluri Frosthand is a 200 years old male mountain dwarf ranger.
He has a bald head and black eyes.
He has rugged, sunburned, gray skin.
He stands 129cm (4'2") tall and has a muscular build.
He has a round, very ugly face with a medium goatee.
He is missing two fingers from his right hand.
(Frosthand, you see.)
He frequently asks questions, bordering Socratic in conversation.

\subsection{Alotel Lithtaur}
\headeritem{Voice}{Say little, growl and threaten.  Alto, speak out the left of your mouth.}
\headeritem{Pronounced}{Al oh tel, Lith to(w)er}
Alotel Lithtaur is a 307 years old female high elf fighter.
She has long, curled, blond hair and green eyes.
She has rough copper skin.
She stands 134cm (5'4") tall and has a muscular build.
She has an sharp, beautiful face.
She smokes the pipe constantly.
A whirling tattoo marks her right hand.
She is missing the tip of her nose, from which a puckered scar runs down past her lip,
  marring her otherwise beautiful face.
She perpetually scowls.
She compares everything to a fight.

  \begin{aloud}
  \label{description:alotel}
  Alotel Lithtaur looks like a fine painting salvaged from a burning castle.
  The high elf has the proud bearing, high cheekbones, and piercing eyes that so often define
    stereotypically attractive elven features.
  But a puckering scar runs from the missing tip of her nose, under her right eye, down to the
    corner of her lips, and around her jaw, leaving her in a perpetual sneer.
  \end{aloud}

\subsection{Garr Bolbec}
\headeritem{Voice}{Clipped, westerner's accent}

Garr Bolbec is a 47 years old male human messenger.
He has very long, curled, auburn hair and cyan eyes.
He has smooth, healthy, bronze skin.
He stands 172cm (5'7") tall and has a round build.
He has an pleasant, round face with a gigantic, braided beard.
He is branded on his left hand, and will never speak of its origin.
He is paranoid.
He knows all the best ways to torture someone.
He is a perfectionist.
